Digital History in Finland, 1488-1828

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

vii) psykologia;yhteiskuntafilosofia;valtiofilosofia;talous;raha;moraali;velvollisuudet;kasvatus

viii) luonnonhistoria;lääketiede;tartuntataudit;eläintiede;kasvitiede;kasvisto;eläimet;eläinsuojelu;eläimistö;eläintaudit;hevonen;maanviljely;maatalous;kalastus

>>>>

vii) psykologia;yhteiskuntafilosofia;valtiofilosofia;talous;raha;moraali;velvollisuudet;kasvatus;maanviljely;maatalous;kalastus

viii) luonnonhistoria;lääketiede;tartuntataudit;eläintiede;kasvitiede;kasvisto;eläimet;eläinsuojelu;eläimistö;eläintaudit;hevonen
